Object Naming in Language and Vision: A Survey and a New Dataset

### 2020-03-17 papers/LREC2020/conclusion.tex

%With respect to naming variation, our
Our current data supports the prediction in theoretical research on object naming that there will often be a preferred (entry-level) name for a given visually presented object.
It tentatively suggests that (a) there is also consistent variation in naming, with an average of almost three elicited names per instance; (b) much of this variation cannot be explained by adopting a hierarchical view, which has been dominant in the psycholinguistic and computational literature; (c) there is high variability in agreement across instances within the same domain.
The latter suggests that there are specific visual characteristics of either the object itself or the visual context in which it appears that trigger variation. With prototypical, idealized pictures of the sort used in traditional studies (see Figure\ \ref{fig:cake}), this observation would not be possible.

>>>>

%With respect to naming variation, our
Our current data supports the prediction in theoretical research on object naming that there will often be a preferred (entry-level) name for a given visually presented object.
It tentatively suggests that (a) there is also consistent variation in naming, with an average of almost three elicited names per instance; (b) much of this variation cannot be explained by adopting a hierarchical view, which has been dominant in the psycholinguistic and computational literature; (c) there is high variability in agreement across instances within the same domain.
The latter suggests that there are specific visual characteristics of either the object itself or the visual context in which it appears that trigger variation. With prototypical, idealized pictures of the sort used in traditional studies (see Figure\ \ref{fig:cake}), this observation would not be possible.
%
These findings also show WordNet's limitations in its use for  visual object naming \cite[a.o.]{Ordonez:2016}: while, for a particular object, synonyms and hypernyms may be retrieved as name alternatives, hierarchically unrelated alternatives cannot, nor does WordNet provide information on object-specific naming preferences.

### 2020-03-17 papers/LREC2020/data-collection.tex
Adds Gemma's corrections

\begin{figure*}[htp]
	\centering
	\includegraphics[scale=.8]{figures/distr_imgs-per-domain_VGMN_v2.png}
% WAS:	\caption{Cumulative histograms of the number of images and names per domain in ManyNames.}
% But it's not really a cumulative histogram
	\caption{Number of images per domain ManyNames. Colors are the original VG names; all high-frequency names are shown, as well as a few lower-frequency names.}
	\label{fig:overview_dataset1}
\end{figure*}

>>>>

\begin{figure*}[htp]
	\centering
	\includegraphics[scale=.8]{figures/distr_imgs-per-domain_VGMN_v2.png}
% WAS:	\caption{Cumulative histograms of the number of images and names per domain in ManyNames.}
% But it's not really a cumulative histogram
	\caption{Number of images and top responses (most frequent name per image), per domain. All high-frequency names are shown, as well as a few lower-frequency names.}
	\label{fig:overview_dataset1}
\end{figure*}
